### 2020-11-17 paper/draft1.tex
added citation and fixed formatting throughout

% \end{abstract}

\section{Definitions}
We model a forecasting competition as $m$ independent events denoted by the independent binary random variables $X_k \in \{0, 1\}$ for $1 \leq k \leq m$. Specifically, let $\theta_k = P(X_k = 1) = 1 - P(X_k = 0)$. For each event, we draw the outcome for the event $x_k \sim X_k$. We say event $k$ occurs when and only when $x_i = 1$. There are $n$ participants in the forecasting competition. Each forecaster independently submits a vector of predictions $y_i \in [0, 1]^m$, such that $y_{i, k}$ is forecaster $i$'s estimate of $\theta_k$. We call these $y_i$ the forecasts of the $i$th forecaster.

@@

\section{Simple average mechanism}
The simplest selection mechanism (and what is often done in practice), we call the simple average mechanism. For this mechanism, we assign each forecaster a score $f_{i, k} = R_q(y_{i, k}, x_k)$ for each event. Then, we assign their final score by summing these over all events, $F_i = \sum_{j=1}^m f_{i, j}$. Finally, we choose the forecaster with the highest cumulative score $\argmax_i F_i$. Each forecaster's cumulative score in this mechanism $\sum_{i=1}^m 1 - (y_{i, j} - x_i)^2$ is an analog for their cumulative accuracy, $m a_j = \sum_{i=1}^m 1 - (y_{i, j} - \theta_j)^2$. However, we will show that this approximation can be flawed.

@@

Assume forecasters remain honest. For single events, the most extreme forecasters will get selected.

For multiple events, we will see that we get similar accuracy bounds as the SHELF mechanism, assuming the forecasters remain honest. In fact, the main advantage of SHELF is that it is as efficient as the Naive mechanism, but also elicits truthful forecasts.

\section{ELF}
The ELF mechanism, introduced in/by [cite elf paper], improves upon the Naive mechanism, by incentivizing forecasters to be truthful. For each event $k$, we hold a lottery to choose a winner. Forecaster $i$ is chosen with probability
\[ f_{i, k} = \frac{1}{n} + \frac{1}{n} \left(R_q(y_{i, k}, x_k) - \frac{\sum_{j\neq i} R_q(y_{j, k}, x_k)}{n-1} \right)\]
This score is the additively normalized quadratic score among all forecasters. A forecaster increasing their own quadratic score increases the chances they win an event, while decreasing the chances others win that event. Let $w_k$ be the winner of event $k$. The ELF mechanism, $M_l$, then chooses $\argmax_i \sum_{k=1}^m \1(w_k = i)$ as the winner of the competition. Essentially, we give the winner of each event a point, and then pick the forecaster who got the most points.

In [elf paper] Theorem 6, they show that ELF is strictly truthful. In Theorem 8, they also show it is accurate. Specifically, that for an accuracy gap of $\epsilon$, ELF has
\[ m_\delta \leq \frac{2(n-1)^2}{\epsilon^2} \ln \left(\frac{4(n-1)}{\delta}\right)\]
For a fixed forecaster accuracy gap and desired mechanism accuracy, the number of events ELF needs is proportional to $n^2 \ln n$. However, this upper bound is not tight, and can be lowered significantly.

Let $F_{i, k}$ be the indicator function for forecaster $i$ winning event $k$. Then, $F_i = \sum_k F_{i, k}$ is the random variable that is the number of events forecaster $i$ wins. The proof of [elf paper] Theorem 8 utilized the Hoeffding bound applied to $F_i$, which assumes they have high variance. However, this is not the case, which leads to an improvement in the lower bound. 
\begin{theorem}[Bernstein's Inequality]
  \label{bernstein}
  Given random variables $X_i$ for $1 \leq i \leq n$ such that $0 \leq X_i \leq 1$ almost surely, let $S = \sum_i X_i$. Then,
  \[ P\left(|S - \E[S]| < t\right) < 2 \: e^{\frac{-t^2 }{2\left(\Var(S) + \frac{t}{3}\right)} } \]
\end{theorem}
\begin{theorem}
  \label{elf_bound}
    For an accuracy gap $\epsilon$, ELF correctly chooses the most accurate forecaster with probability at least $1 - 4 (n-1) e^{-\frac{m \epsilon}{6(n - 1)}}$.
\end{theorem}
\emph{Proof:} Note that for any single event $k$, every forecaster wins with probability at best $\frac{2}{n}$, and at worst $\frac{1}{n} - \frac{1}{n(n-1)}$ (achieved when $y_i = 1$, $y_{j\neq i} = 0$, and $x_i = 1$). Since $F_{i, k}$ is just a binary random variable, it will have highest variance when it's expectation is as close to $\frac{1}{2}$ as possible. For nontrivially small $n$, this will mean its expectation is $\frac{2}{n}$ (or equivalently $P(F_{i, k} = 1) = \frac{2}{n}$), so its variance will be at most $\frac{2(n-2)}{n^2}$. So we have $\Var(F_{i, k}) \leq \frac{2(n-2)}{n^2} < \frac{2}{n}$.

@@

Applying Theorem \ref{bernstein}, we have
\begin{align*}
    P\left(\left| F_i - \E[F_i]\right| < \frac{m \epsilon}{2(n - 1)} \right) 
    &< 2 \: e^{\frac{-\left(\frac{m \epsilon}{2(n - 1)}\right)^2 }{2\left(\frac{2m}{n} + \frac{m \epsilon}{6(n - 1)}\right)}} \\
    &< 2 \: e^{\frac{-\left(\frac{m \epsilon}{2(n - 1)}\right)^2 }{2\left(\frac{m}{n-1}(2 + \frac{\epsilon}{6}) \right)}} \\
    &= 2 \: e^{\frac{-\frac{m \epsilon^2}{2(n - 1)} }{(2 + \frac{\epsilon}{6})}} \\
    &< 2 \: e^{-\frac{m \epsilon^2}{5(n - 1)} }  \numberthis \label{elf_bernstein} 
\end{align*}
And similarly for $F_j$. Putting both of those cases together, we have by the union bound
\begin{align*}
  P(F_j \geq F_i) &= P\left(\left(F_j - \E[F_j] < \frac{m \epsilon^2}{2(n - 1)}\right) \cup \left(\E[F_i] - F_i < \frac{m \epsilon^2}{2(n - 1)} \right) \right) \\
  &\leq P\left(F_j - \E[F_j] < \frac{m \epsilon^2}{2(n - 1)}\right) + P\left(\E[F_i] - F_i < \frac{m \epsilon^2}{2(n - 1)} \right) \\
  &\leq 4 \: e^{-\frac{m \epsilon^2}{5(n - 1)} }
\end{align*}
Using the union bound over all $j$, we have
\begin{align*}
  P\left(M_l(y_1, ..., y_n, x) = i\right)
  &= 1 - \sum_{j\neq i} P\left(M_l(y_1, ..., y_n, x) = j\right) \\
  &\geq 1 - \sum_{j\neq i} P\left(F_j \geq F_i\right) \\
  &\geq 1 - 4 (n-1) e^{-\frac{m \epsilon^2}{5(n - 1)}} 
\end{align*}
\hfill\QED

Assigning this probability to $1 - \delta$, we see that for a fixed $n, \epsilon$, ELF will choose the correct forecaster with probability at least $1 - \delta$ if $m$ is large enough for the above inequality to hold. Solving it for $m$, we get the minimum such satisfying value
\[m_\delta \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right) \]

\section{SHELF}
For this mechanism, we let the binary random variable $X_{i, k}$ be 1 with probability $R_q(y_{i, k}, x_i)$, and 0 otherwise. Then, for each event $k$ we assign forecaster $i$ the score $f_{i, k} = X_{i, k}$ obtained by sampling this variable. Finally, we assign their final score by summing these over all events, $F_i = \sum_{j=1}^m f_{i, j}$, then chose the forecaster with the highest $F_i$, breaking ties uniformly at random.

\subsection{Truthfulness}
(following section 4.2, theorem 4) For a single event with true probability $\theta$, every forecaster will either win 1 or 0 events. The probability that their final score is 1 will just be their expected score for the single event. Therefore, to maximize their final score, each forecaster must maximize their expected score for the single event. Their score is just $\E_{x \sim \theta}(R_q(y_i, x)) = \E_{x \sim \theta}(1 - (y_i - x)^2)$. This is maximized when $y_i = \theta$, so the mechanism is truthful. (what theorem 4 does) We can also see this directly be noting that $R_q$ is a strictly proper scoring rule, so its expectation is maximized when $y_i = \theta$.

\textbf{Theorem}: SHELF is truthful for $m \geq 1$ events.\\\\
Proof. For each forecaster $j \in [1, n]$ fix forcaster's report.\\\\
S'pose that for some forecaster $i$, $i$'s report on some subset of events, where $k \in [1, m]$ denotes the size of this subset, does not maximize their expected score for any of those individual events.\\
Let $k^\prime$ be one of those events.\\\\
We will now show that $i$ will maximize their probability of being chosen as the best forecaster in the SHELF mechanism iff they alter their $k$ reports to maximize their expected score on each $k$ events. A guiding intuition here would be as follows: The higher the expected score a forecaster has on a given event, the higher the probability that SHELF awards them a point on this specific event, and the only way to maximize one's probability of being selected as the best forecaster is to increase the number of points they are awarded. Therefore, for a single independent event, increasing one's expected score will either increase the probability of being selected as the best forecaster or leave it unchanged, and it does so without altering results of any other event. In this way, we will show that being truthful for a singular event will always increase one's probability of being selected as the best forecaster. We can then repeat this process for each untruthful report to maximize the probability of being selected as the best forecaster.\\\\
Formally, we will analyze three cases relating to the context provided by the $m - 1$ events other than $k^\prime$.\\\\
Let $V(i)$ denote the number of points forecaster $i$ has accrued.\\
Let $f_{i,k}$ denote the probability forecaster $i$ scores a point on event $k$.\\

\begin{enumerate}
    \item Some forecaster $j$ scores at least two more points than $i$, OR $i$ scores at least two more points than any other forecaster.\\
    $$\exists j \in [1,m] \text{ s.t. } j \ne i \text{ and } V(j) - V(i) \geq 2$$ 
    $$OR$$
    $$\forall j \in [1,m] \text{ s.t. } j \ne i; V(i) - V(j) \geq 2$$
    For this case, $i$'s probability of being selected as the best forecaster is either $1$ or $0$. It is also unaffected by being truthful or not in $k^\prime$, because gaining, or failing to gain, $1$ point in this context is not enough to alter the outcome as only the forecaster with the most number of points is chosen as the best forecaster with ties broken uniformly.\\\\

@@

From proposition 2, we have that $E_{x \sim \theta}(R_q(y, x)) = R_q(y, \theta) + \theta^2 - \theta$. Additionally, for a single event, a forecaster's accuracy $a_i$ is by definition just $R_q(y, \theta)$. So, $E_{x \sim \theta}(R_q(y, x)) = a_i + \theta^2 - \theta$. For a single event with probability $\theta$, forecaster $i$'s expected score is $\E_{x \sim \theta} f_i = E_{x \sim \theta}(R_q(y_i, x)) = a_i + \theta^2 - \theta$.

\subsection{Truthfulness for a single event}
(section 4.3, proposition 5).  For forecaster $i$ to be selected, they either need to have $f_i = 1$, and then be chosen uniformly at random from all others who scored 1, or everyone must score 0 and they will be chosen uniformly at random. In the first case, the expected number of other forecasters who also score 1 is $\sum_{i' \neq i} \E_{x \sim \theta} f_{i'} = \sum_{i' \neq i} (a_{i'} + \theta^2 - \theta) = (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}$. Then, the probability that forecaster $i$ is chosen is 
\[
  P(f_i = 1) \frac{1}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}} = \frac{a_i +\theta^2 - \theta}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}}
\]
In the other case, the probability $i$ wins is just 
\[
  \frac{1}{n} \prod_{i} P(f_i = 0) = \frac{\prod_i (1 - a_i -\theta^2 + \theta)}{n}
\]

There's probably a better way to do this... Actually coming back to this I'm not even sure that the first step is allowed (using expected number of winners directly instead of summing over cases)

\subsection{Truthfulness for multiple events}
multiple events: (section 5.3, theorem 8)
Let $a_i \geq a_j + \epsilon$ for all $j\neq i$. Like in theorem 8, we first bound the expected number of events won that $i$ exceeds $j$ by. 
\begin{align*}
  \E \left( \sum_{k=1}^m f_{i, k}\right) - \E \left( \sum_{k=1}^m f_{j, k}\right)
  &= \left( \sum_{k=1}^m \E f_{i, k}\right) - \left( \sum_{k=1}^m \E f_{j, k}\right)\\
  &= \sum_{k=1}^m \left(\E (f_{i, k}) - \E (f_{j, k})\right)\\
  &= \sum_{k=1}^m \left((a_i + \theta_k^2 - \theta_k) - (a_j + \theta_k^2 - \theta_k)\right)\\
  &= \sum_{k=1}^m \left(a_i - a_j\right)\\
  &\geq \sum_{k=1}^m \epsilon\\
  &=m \epsilon
\end{align*}
If $F_j \geq F_i$, then either $\E(F_i) - F_i \geq \frac{m \epsilon}{2}$ or $F_j - \E(F_j) \geq \frac{m \epsilon}{2}$. By Hoeffding's, we can upper bound the probability of each of these events by $2 e^{-\frac{2 (\frac{m \epsilon}{2})^2}{m}} = 2 e^{\frac{- m \epsilon^2}{2}}$. Using the union bound, the probability that either of those events occurs is twice this, or $4 e^{\frac{- m \epsilon^2}{2}}$.

Using the union bound again over all $j \neq i$, we have 
\[
1 - \delta = P(M(y_1, ..., y_n, x) = i) = 1 - \sum_{j \neq i} P(F_j \geq F_i) = 1 - 4 (n-1) e^{\frac{- m \epsilon^2}{2}}
\]
Letting this quantity be $1 - \delta$ and solving for $m$, we see that this mechanism correctly chooses forecaster $i$ with probability $1 - \delta$ when $m$ is large enough to satisfy the inequality. Solving for $m$ gives us the minimum such value, which is an upper bound of $m_\delta$ for SHELF.
\[ m_\delta \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta} \]

% \begin{thebibliography}{99}

% \end{thebibliography}

>>>>

% \end{abstract}
\section{Name???}
- SHELF\\
- GNOME\\
- ???

keywords: event, forecast, voting

EFV

\section{Definitions}
The definitions borrow heavily in both content and organization from previous work \cite{elf}.

We model a forecasting competition as $m$ independent events denoted by the independent binary random variables $X_k \in \{0, 1\}$ for $1 \leq k \leq m$. Specifically, let $\theta_k = P(X_k = 1) = 1 - P(X_k = 0)$. For each event, we draw the outcome for the event $x_k \sim X_k$. We say event $k$ occurs when and only when $x_i = 1$. There are $n$ participants in the forecasting competition. Each forecaster independently submits a vector of predictions $y_i \in [0, 1]^m$, such that $y_{i, k}$ is forecaster $i$'s estimate of $\theta_k$. We call these $y_i$ the forecasts of the $i$th forecaster.

@@

\section{Simple average mechanism}
A simple selection mechanism that is often done in practice, we will call the simple average mechanism $M_s$. For this mechanism, we assign each forecaster a score $f_{i, k} = R_q(y_{i, k}, x_k)$ for each event. Then, we assign their final score by summing these over all events, $F_i = \sum_{j=1}^m f_{i, j}$. Finally, we choose the forecaster with the highest cumulative score $M_s(y, x) = \argmax_i F_i$. The idea of this mechanism is that each forecaster's final score in this mechanism is $F_i = \sum_{i=1}^m 1 - (y_{i, j} - x_i)^2$ is an analog for their cumulative accuracy, $m a_i = \sum_{k=1}^m 1 - (y_{i, k} - \theta_k)^2$. Therefore, the forecaster with the highest score will correlate to the forecaster with the highest accuracy. However, we will show that this is not necessarily the case.

@@

\subsection{Accuracy}
Even though $M_s$ is not truthful, we assume that forecasters still report their true beliefs $\hat \theta_i$. For a single event, the most extreme forecasters will always get selected. For example, if the single outcome is $x = 0$, the forecaster with the minimum $\hat \theta_i $ will have the highest score, so they will always win. Similarly if $x = 1$, the highest belief forecaster will always win.

However, for multiple events, the averaging starts to favor more forecasters. We will see that we get a similar $m_\delta$ as the SHELF mechanism introduced later, assuming the forecasters remain truthful. In fact, the main advantage of SHELF is that it is as efficient as $M_s$ while also being truthful.

\section{ELF}
\newcommand{\elf}{M_{\mathrm{ELF}}}
The ELF mechanism $\elf$ \cite{elf}, improves upon $M_s$, by incentivizing forecasters to be truthful. For each event $k$, we hold a lottery to choose a winner. Forecaster $i$ is chosen with probability
\[ f_{i, k} = \frac{1}{n} + \frac{1}{n} \left(R_q(y_{i, k}, x_k) - \frac{\sum_{j\neq i} R_q(y_{j, k}, x_k)}{n-1} \right)\]
This score is the additively normalized quadratic score among all forecasters. A forecaster increasing their own quadratic score increases the chances they win an event, while decreasing the chances others win that event. Let $w_k$ be the winner of event $k$. Then we choose the forecaster $\elf(y, x) = \argmax_i \sum_{k=1}^m \1(w_k = i)$ as the winner of the competition. Essentially, we give the winner of each event lottery a point, and then pick the forecaster who got the most points as the overall winner.

In Theorem 6 of \cite{elf}, it is proven that $\elf$ is strictly truthful. In Theorem 8 of the same paper, they also upper bound $m_\delta$ by showing 
\[ m_\delta(\elf, n, \epsilon) \leq \frac{2(n-1)^2}{\epsilon^2} \ln \left(\frac{4(n-1)}{\delta}\right)\]
For a fixed forecaster accuracy gap and desired mechanism accuracy, the number of events ELF needs to consistently choose the right forecaster is proportional to $\frac{1}{\epsilon^2} n^2 \ln n$. However, this upper bound is not tight.

Let $F_{i, k}$ be the indicator function for forecaster $i$ winning the lottery for event $k$. Then, $F_i = \sum_k F_{i, k}$ is the random variable that is the number of events forecaster $i$ wins. The proof of Theorem 8 \cite{elf} utilized the Hoeffding bound applied to $F_i$, which assumes they have high variance. However, this is not the case, and utilizing that fact gives an improvement in the lower bound. 
\begin{theorem}[Bernstein's Inequality]
  \label{bernstein}
  Given random variables $X_i$ for $1 \leq i \leq n$ such that $0 \leq X_i \leq 1$ almost surely, let $S = \sum_i X_i$. Then,
  \[ P\left(|S - \E[S]| < t\right) < 2 \: e^{\frac{-t^2 }{2\left(\Var(S) + \frac{t}{3}\right)} } \]
\end{theorem}
\begin{theorem}
  \label{elf_bound}
    $m_\delta(\elf, n, \epsilon) \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right)$
    % For an accuracy gap $\epsilon$, ELF correctly chooses the most accurate forecaster with probability at least $1 - 4 (n-1) e^{-\frac{m \epsilon}{6(n - 1)}}$.
\end{theorem}
\emph{Proof:} Note that for any single event $k$, every forecaster wins with probability at best $\frac{2}{n}$, and at worst $\frac{1}{n} - \frac{1}{n(n-1)}$ (achieved when $y_i = 1$, $y_{j\neq i} = 0$, and $x_i = 1$). Since $F_{i, k}$ is just a binary random variable, it will have highest variance when it's expectation is as close to $\frac{1}{2}$ as possible. For nontrivially small $n$, this will mean its expectation is $\frac{2}{n}$ (or equivalently $P(F_{i, k} = 1) = \frac{2}{n}$), so its variance will be at most $\frac{2(n-2)}{n^2}$. So we have $\Var(F_{i, k}) \leq \frac{2(n-2)}{n^2} < \frac{2}{n}$.

@@

Applying Theorem \ref{bernstein}, we have
\begin{align*}
    P\left(\left| F_i - \E[F_i]\right| < \frac{m \epsilon}{2(n - 1)} \right) 
    &< 2 \: e^{\frac{-\left(\frac{m \epsilon}{2(n - 1)}\right)^2 }{2\left(\frac{2m}{n} + \frac{m \epsilon}{6(n - 1)}\right)}} \\
    &< 2 \: e^{\frac{-\left(\frac{m \epsilon}{2(n - 1)}\right)^2 }{2\left(\frac{m}{n-1}(2 + \frac{\epsilon}{6}) \right)}} \\
    &= 2 \: e^{\frac{-\frac{m \epsilon^2}{2(n - 1)} }{(2 + \frac{\epsilon}{6})}} \\
    &< 2 \: e^{-\frac{m \epsilon^2}{5(n - 1)} }  \numberthis \label{elf_bernstein} 
\end{align*}
And similarly for $F_j$. Putting both of those cases together, we have by the union bound
\begin{align*}
  P(F_j \geq F_i) &= P\left(\left(F_j - \E[F_j] < \frac{m \epsilon^2}{2(n - 1)}\right) \cup \left(\E[F_i] - F_i < \frac{m \epsilon^2}{2(n - 1)} \right) \right) \\
  &\leq P\left(F_j - \E[F_j] < \frac{m \epsilon^2}{2(n - 1)}\right) + P\left(\E[F_i] - F_i < \frac{m \epsilon^2}{2(n - 1)} \right) \\
  &\leq 4 \: e^{-\frac{m \epsilon^2}{5(n - 1)} }
\end{align*}
Using the union bound over all $j$, we have
\begin{align*}
  P\left(M_l(y_1, ..., y_n, x) = i\right)
  &= 1 - \sum_{j\neq i} P\left(M_l(y_1, ..., y_n, x) = j\right) \\
  &\geq 1 - \sum_{j\neq i} P\left(F_j \geq F_i\right) \\
  &\geq 1 - 4 (n-1) e^{-\frac{m \epsilon^2}{5(n - 1)}} 
\end{align*}

Assigning this probability to $1 - \delta$, we see that for a fixed $n, \epsilon$, ELF will choose the correct forecaster with probability at least $1 - \delta$ if $m$ is large enough for the above inequality to hold. Solving it for $m$, we get the minimum such satisfying value
\[m_\delta \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right) \]
\hfill\QED

\section{SHELF}
\newcommand{\shelf}{M_{\mathrm{SHELF}}}

For this mechanism, we let the binary random variable $X_{i, k}$ be 1 with probability $R_q(y_{i, k}, x_i)$, and 0 otherwise. Then, for each event $k$ we assign forecaster $i$ the score $f_{i, k} = X_{i, k}$ obtained by sampling this variable. Finally, we assign their final score by summing these over all events, $F_i = \sum_{j=1}^m f_{i, j}$, then chose the forecaster with the highest score $\shelf(y, x) = \argmax_i F_i$, breaking ties uniformly at random.

\subsection{Truthfulness}
For a single event with true probability $\theta$, every forecaster will either win 1 or 0 events. The probability that their final score is 1 will just be their expected score for the single event. Therefore, to maximize their final score, each forecaster must maximize their expected score for the single event. Their score is just $\E_{x \sim \theta}(R_q(y_i, x)) = \E_{x \sim \theta}(1 - (y_i - x)^2)$. This is maximized when $y_i = \theta$, so the mechanism is truthful. (what theorem 4 does) We can also see this directly be noting that $R_q$ is a strictly proper scoring rule, so its expectation is maximized when $y_i = \theta$.

\begin{theorem}
  \label{shelf_truthful}
    $\shelf$ is truthful for $m \geq 1$ events.
\end{theorem}
\emph{Proof:} For each forecaster $j \in [1, n]$ fix forcaster's report.

S'pose that for some forecaster $i$, $i$'s report on some subset of events, where $k \in [1, m]$ denotes the size of this subset, does not maximize their expected score for any of those individual events.\\
Let $k^\prime$ be one of those events.

We will now show that $i$ will maximize their probability of being chosen as the best forecaster in the SHELF mechanism iff they alter their $k$ reports to maximize their expected score on each $k$ events. A guiding intuition here would be as follows: The higher the expected score a forecaster has on a given event, the higher the probability that SHELF awards them a point on this specific event, and the only way to maximize one's probability of being selected as the best forecaster is to increase the number of points they are awarded. Therefore, for a single independent event, increasing one's expected score will either increase the probability of being selected as the best forecaster or leave it unchanged, and it does so without altering results of any other event. In this way, we will show that being truthful for a singular event will always increase one's probability of being selected as the best forecaster. We can then repeat this process for each untruthful report to maximize the probability of being selected as the best forecaster.\\\\
Formally, we will analyze three cases relating to the context provided by the $m - 1$ events other than $k^\prime$.

Let $V(i)$ denote the number of points forecaster $i$ has accrued.\\
Let $f_{i,k}$ denote the probability forecaster $i$ scores a point on event $k$.\\

\begin{enumerate}
    \item Some forecaster $j$ scores at least two more points than $i$, OR $i$ scores at least two more points than any other forecaster.\\
    $$\exists j \in [1,m] \text{ s.t. } j \ne i \text{ and } V(j) - V(i) \geq 2$$ 
    $$OR$$
    $$\forall j \in [1,m] \text{ s.t. } j \ne i; V(i) - V(j) \geq 2$$
    For this case, $i$'s probability of being selected as the best forecaster is either $1$ or $0$. It is also unaffected by being truthful or not in $k^\prime$, because gaining, or failing to gain, $1$ point in this context is not enough to alter the outcome as only the forecaster with the most number of points is chosen as the best forecaster with ties broken uniformly.

@@

% From Proposition 2 of \cite{elf}, we have that $E_{x \sim \theta}(R_q(y, x)) = R_q(y, \theta) + \theta^2 - \theta$. Additionally, for a single event, a forecaster's accuracy $a_i$ is by definition just $R_q(y, \theta)$. So, $E_{x \sim \theta}(R_q(y, x)) = a_i + \theta^2 - \theta$. For a single event with probability $\theta$, forecaster $i$'s expected score is $\E_{x \sim \theta} f_i = E_{x \sim \theta}(R_q(y_i, x)) = a_i + \theta^2 - \theta$.

% \subsection{Truthfulness for a single event}
% (section 4.3, proposition 5).  For forecaster $i$ to be selected, they either need to have $f_i = 1$, and then be chosen uniformly at random from all others who scored 1, or everyone must score 0 and they will be chosen uniformly at random. In the first case, the expected number of other forecasters who also score 1 is $\sum_{i' \neq i} \E_{x \sim \theta} f_{i'} = \sum_{i' \neq i} (a_{i'} + \theta^2 - \theta) = (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}$. Then, the probability that forecaster $i$ is chosen is 
% \[
%   P(f_i = 1) \frac{1}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}} = \frac{a_i +\theta^2 - \theta}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}}
% \]
% In the other case, the probability $i$ wins is just 
% \[
%   \frac{1}{n} \prod_{i} P(f_i = 0) = \frac{\prod_i (1 - a_i -\theta^2 + \theta)}{n}
% \]

% There's probably a better way to do this... Actually coming back to this I'm not even sure that the first step is allowed (using expected number of winners directly instead of summing over cases)

% \subsection{Truthfulness for multiple events}
\begin{theorem}
  \label{shelf_bound}
    $m_\delta(\shelf, n, \epsilon) \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta}$
\end{theorem}
\emph{Proof:} This proof is a slight modification of the proof of Theorem 8 in \cite{elf}.

We first bound the difference in the expected number of wins of $i^*$ and $j$, for any $j \neq i^*$. 
\begin{align*}
  \E \left( \sum_{k=1}^m f_{i^*, k}\right) - \E \left( \sum_{k=1}^m f_{j, k}\right)
  &= \left( \sum_{k=1}^m \E f_{i^*, k}\right) - \left( \sum_{k=1}^m \E f_{j, k}\right)\\
  &= \sum_{k=1}^m \left(\E (f_{i^*, k}) - \E (f_{j, k})\right)\\
  &= \sum_{k=1}^m \left((a_{i^*} + \theta_k^2 - \theta_k) - (a_j + \theta_k^2 - \theta_k)\right)\\
  &= \sum_{k=1}^m \left(a_{i^*} - a_j\right)\\
  &\geq \sum_{k=1}^m \epsilon\\
  &=m \epsilon
\end{align*}
If $F_j \geq F_{i^*}$, then either $\E(F_{i^*}) - F_{i^*} \geq \frac{m \epsilon}{2}$ or $F_j - \E(F_j) \geq \frac{m \epsilon}{2}$. By Hoeffding's, we can upper bound the probability of each of these events by $2 e^{-\frac{2 (\frac{m \epsilon}{2})^2}{m}} = 2 e^{\frac{- m \epsilon^2}{2}}$. Using the union bound, the probability that either of those events occurs is twice this, or $4 e^{\frac{- m \epsilon^2}{2}}$.

Using the union bound again over all $j \neq i$, we have 
\begin{align*}
  P(\shelf(y, x) = i) &= P(F_{i^*} > F_j \quad \forall j \neq i^*) \\
                      &\geq 1 - \sum_{j\neq i^*} P(F_{i^*} \leq F_j) \\
                      &= 1 - 4 (n-1) e^{\frac{- m \epsilon^2}{2}}
\end{align*}

Letting this quantity be $1 - \delta$ and solving for $m$, we see that this mechanism correctly chooses forecaster $i$ with probability $1 - \delta$ when $m$ is large enough to satisfy the inequality. Therefore
\[ m_\delta(\shelf, n, \epsilon) \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta} \]
\hfill \QED

Comparing this to the result of Theorem \ref{elf_bound}, we see that $\shelf$ is much more efficient than $\elf$. We can also directly apply the proof of Theorem \ref{shelf_bound} to $M_s$, since the mean and variance of $F_i$ is the same in both cases. Therefore, $m_\delta(\shelf, n, \epsilon) = m_\delta(M_s, n, \epsilon)$.

\begin{thebibliography}{99}
\bibitem{elf} Witkowski, Freeman  \emph{Incentive-Compatible Forecasting Competitions} \url{https://las.inf.ethz.ch/files/witkowski-etal-aaai2018.pdf}.

\end{thebibliography}
